Fake Clicks on Video Ads

### 2015-05-05 doc/paper.tex
Heron's update for second half part

\maketitle

@@

\section{Introduction}
Association of National Advertisers (ANA) has estimated that artificial views on advertisement will cost advertiser 6.3 billion dollars in 2015~\cite{c1}. ANA also concluded that roughly 23\% of views on advertisements are views that are generated by bots and not real internet users~\cite{c1}. The surprising fact is these artificial views are present in not only armature or personal publishing sites but are also in professional sites which are operated by respected businesses such as Ford, Intel, MasterCard, and Wendy’s~\cite{c3}. The guardian news article stated that about 25\% of artificial views happen on premium sites which are in the top 1000 visited sites in the world~\cite{c3}. These facts can imply two things: 1. Publishers can’t stop fake views/clicks alone. 2. Hackers are building sophisticated bots which emulates user characteristic that are tricking the current defense system.

If 25\% of artificial views happen on premium sites, this means the other 75\% are on armature or non-premium sites. Although it is unclear what defense systems the premium sites are using to defend against fake views, it is clear that the publishers alone can’t stop fake views by themselves. In a recent study in 2014, 181 real video advertisements were observed over 60 days~\cite{c19}. The research found that 23\% of the views of advertisements came from bots. 67\% of the fake views came from residential homes and 58\% were using Microsoft Explorer 6, which has been discontinued since 2008~\cite{c19}. These facts imply that the hackers are infecting vulnerable computers and planting bots to generate artificial views on various advertisements. Indeed this was the case with “Operation Ghost Click” in 2011~\cite{c3, c4}. The U.S. FBI captured 6 Estonian Nationals who were installing rogue DNS servers to infect local DNS cache on vulnerable computers around the world. The rogue servers infected 4 million computers in 100 different countries, 500,000 in the U.S., to redirect users to various sites which hosted advertisements that were linked to the 6 Estonians~\cite{c4}. For example, if the infected computer browses “www.microsoft.com”, user would be redirected to a site that is similar to Microsoft’s site but with random advertisements. The 6 Estonians were able to illegally collect 14 million dollars from the advertisers~\cite{c4}.

@@

In this paper, we used 4 services that claim to generate view counts on videos hosted by YouTube and Dailymotion. The prices of their services ranged from 3 to 300 dollars and offered view counts from 50 to 50,000. We purchased the cheapest service ranging from 3 to 8 dollars for 500 to 5000 views. Only three services were able to deliver their view counts in span of 2 to 7 days while one service still haven’t deliver as of May 4$^{th}$ 2015. The statistical data from YouTube and Dailymotion were limited; however, we did find some interesting data as well as verify some information that were stated in other research papers about fake views. Lastly, we wrote some programs which mimics the characteristics of traffics that were analyzed from services that generates view counts for monetary payment. Our programs were tested on videos hosted in YouTube.

@@

\subsection{Buildmyviews.org}
The first service that we used was from http://buildmyviews.org. The IP address of this website is 166.62.5.1, hosted by godaddy.com located in Scottsdale~\cite{c6} U.S. The site’s front page is displayed in figure 1 below. It doesn’t look like a premium website but it does look legitimate but not actively managed. This service offered view counts for videos only hosted by YouTube, but they offered 3 different options of view counts.

@@

Aside from the view counts, this service also offered to generate comments on YouTube video. This website claims to offer 24/7 customer support via emails and also chat services. The chat services didn’t seems to work as no one replied when we started to use their chat service screen. Moreover, when we sent an email asking about their basic operation on March 2, 2015, we didn’t receive any reply as of April 2$^{nd}$, 2015. However, when we purchase their service of 1000 views for 3 dollars, we did receive a confirmation email from socialwarehouseorg@gmail.com with the name ``Kevin M''.

@@

The second service that we used was from http://portal.dalisocial.com/. The IP address of this website is 104.24.112.186, hosted by CloudFlare, Inc. located in San Francisco U.S. We needed to register before using the service but we used a random name and an email to get into the site. Email confirmation wasn’t needed and this site didn’t looked professionally managed. However, it offered services across different social media sites. This site offered but not limited to:

@@

The Dalisocial site did not offer granular services like buildmyviews.org. For example, it just offered one option to purchase 5000 YouTube views for 7 dollars within 3 days. We noticed the most of the link on the site didn’t work. For example, nothing happened when we clicked the ``Contact Us'', ``About Us'', and ``Blog'' link. The only link that worked was the ``Login'' which directs to a page to purchase services. We did receive an email when we registered and purchase their service of 5000 views for 7 dollars. The email was from noreply@dalisocial.com.

@@

In this section, we analyzed data which was generated by the 3 services, since one vendor failed to deliver, that we mentioned in section III. We uploaded 4 different videos: 3 in YouTube and 1 in Dailymotion. All videos were about 60 seconds long and each were tested using different services. Since we can only use statistical data provided by YouTube and Dailymotion, there was limitation of data which could be observed and analyzed. For example, we couldn’t observed the exact IP address but just the general physical location. However, we were able to observe key information such as average duration watched, method of access, what OS was used, and the view counts per day; to come up with the following analysis:

@@

\begin{enumerate}
  \item SocialWarrior.net used same or very similar type of bot from Buildmyviews.org to generate the views as we observe similar characteristics.
  \begin{itemize}
    \item Russia accounts for the highest number of views followed by Argentina.
    \item View length was different but still constant at 57 seconds.
    \item Used the same access method: ``YouTube watchpage''.
    \item All views used Blackberry OS.
  \end{itemize}
  \item The bots have viewed almost whole duration of the video hosted in YouTube, 57 seconds.
  \item It took significantly longer to deliver view counts on video hosted by Dailymotion. The 2000 view counts on YouTube was delivered in 48 hours while it took about a week to deliver view counts on Dailymotion.
  \item The view counts on Dailymotion wasn’t generated systematically. We did not find a definite pattern but views were generated once or twice every 7-14 minutes for few hours, then go into a long pause, then start generating views again every 7-14 minutes.
\end{enumerate}

@@

\begin{enumerate}
  \item As already mentioned, SocialWarrior.net may used same or very similar type of bot from Buildmyviews.org as we observed similar characteristics.
  \item Assuming SocialWarrior,net and Buildmyviews.org used the same type of bot, the bots are flexible to view the whole or just part of the video.
  \item YouTube and Dailymotion use different system to count views. That is why it took only 48 hours to deliver 2000 views on YouTube while it took about a week to deliver only 500 views on Dailymotion.
  \item SocialWarrior.net used different methods to generate views on YouTube and Dailymotion. On Dailymotion, only the time can be observed, we didn’t receive other data such as the source locaton, OS, and access method. However, based on the time data, SocialWarrior.net could have used real users to generate view counts on Dailymotion, as it isn’t hard to generate 500 views in period of 7 days.
\end{enumerate}

@@

\begin{enumerate}
  \item The view sources were evenly distributed especially in the Middle East: Egypt, Saudi Arabia and Turkey (Fig. \ref{7a}).
  \item All bots viewed the entire video, 60 seconds.
  \item 51\% of views are from “YouTube homepage”, meaning, the video was accessed via link suggested by YouTube.  This is only possible if you have a YouTube account~\cite{c21}.
  \item 49\% of bot views are direct views, same method as previous 2 services used.
  \item 99\% of the traffic is from computers, mostly from Windows OS, but MAC and Linux also had small presence (less than 2\% each).
  \item 18 out of 5000 views from gaming consoles, from Saudi Arabia and Germany.
  \item 17 out of 5000 views from mobile devices; Android and IPhone but no Blackberry.
\end{enumerate}

@@

Here we tried to use our own code to generate artificial view counts on videos hosted in YouTube. Before writing the code, we studied how YouTube view counting system works. The following is the list of what we’ve learned:

@@

In order to generate YouTube views, we've tried publically available Javacript codes: PhantomJS and SeleniumHQ. PhamtonJS didn’t work to generate views on YouTube since it doesn’t support Adobe Flash Player; SeleniumHQ, however, was successful as it was tested on normal client machines as well as Ubuntu Server.

Since we didn’t need the browser popup displaying YouTube videos, we used Xvfb (Virtual framebuffer X server for X Version 11) to buffer screen display in the background while taking snapshots for information analysis and debugging purposes.

@@

\begin{figure}
  \centering
  \includegraphics[width=3.0in]{flowchart}
  \caption{Flowchart of our fake click generating code}
\end{figure}

Refer to our Github repository for the actual code (https://github.com/heronyang/youtube\_fake\_view). With our code, we were able to generate at least 301 view counts on videos hosted in YouTube, using one machine with one user agent. This is because YouTube view counting system analyzes the view counts after 301 and determined that the views generated by our code isn’t from a real user. In our next section, we explain how we used our code in various ways to implement more unique IP addresses, user agents, and VPN connections to pass the 301 views on videos hosted in YouTube.

@@

We are assuming YouTube view counting system checks user agent information since this could be an obvious indicator to detect bot traffic. For example, it is highly unlikely that a video suddenly gets viewed 1000 times with the exact same user agent string. There are too many different OS/browser combination available for 1000 random users to have the same user string, and since one user wouldn’t constantly view the same video 1000 times, this could be an obvious sign of bot traffic. Therefore, we tested our code using 526 different user agent strings to see if we can generate more than 301 artificial view counts on video hosted in YouTube.

@@

Setup environment where this experiment was executed:
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item OS: Ubuntu 14.01 Server
  \item Duration: From April 28$^{th}$ 2030-2300 (3hr, 30min)
  \item Public IP: 172.31.20.23
  \item User agent: 526 different user agents
  \item 150-200 views every hour
\end{itemize}

@@

\subsubsection*{Findings}
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item View count quickly generated to 301 within one hour but unchanged as of May 4$^{th}$ 2015.
  \item 5 public IP addresses isn’t enough to pass 301 view count.
\end{itemize}

@@

Setup environment where this experiment was executed:
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item OS: MAC OS X v10.10
  \item Duration: From April 30th 1730-0330 (10 hrs)
  \item Browser: Firefox 37.0.2
  \item 50-60 views every hour
\end{itemize}

\subsubsection*{Findings}
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item View count is still stuck at 301.
  \item Source IP is visible via flash browser plugin~\cite{c14}. This means that YouTube knows where the actual request is coming from; thus, anonymity isn’t possible using TOR when viewing videos in YouTube.
\end{itemize}

@@

\subsubsection*{Findings}
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item View count is still stuck at 301.
  \item Using popular VPN connection doesn’t matter.
\end{itemize}

@@

Lastly, YouTube counting system isn’t perfect as it proven to allow both false positive and false negative view counts in our research. We were able to prove it allows false positive view counts by using the 4 services mentioned in section 2 \& 3. Moreover, for the videos that were stuck on 301+ views, we view the same videos manually and see if the view count will go over 301. The view counts didn’t change even after we manually view the videos; therefore, we assume that YouTube’s counting
system is also vulnerable to false negative view counts.

@@

\begin{enumerate}
  \item The data provided by YouTube isn’t enough to technically evaluate the characteristics of artificial view generating bots. The limitation of the data is already mentioned on Traffic Analysis section of the research. Perhaps, we could request granular statistical information from YouTube to provide the following:
  \begin{itemize}
    \item Exact time the views were generated
    \item The public source IP address
    \item User agent string for each view
  \end{itemize}
  \item We didn’t have enough resources. As observed from the 3 artificial view generating services, bots were present from at least 20 different countries which was able to pass the 301 view count on YouTube video within 48 hours. Perhaps if we can partner with other universities around the world, we can run our code in various places to see if we can also pass the 301 view count.
\end{enumerate}

>>>>

\maketitle
\thispagestyle{plain} % add page number
\pagestyle{plain}

@@

\section{Introduction}
Association of National Advertisers (ANA) has estimated that artificial views on advertisement will cost advertiser 6.3 billion dollars in 2015~\cite{c1}. ANA also concluded that roughly 23\% of views on advertisements are views that are generated by bots and not real internet users~\cite{c1}. The surprising fact is these artificial views are present in not only armature or personal publishing sites but are also in professional sites which are operated by respected businesses such as Ford, Intel, MasterCard, and Wendy’s~\cite{c3}. The guardian news article stated that about 25\% of artificial views happen on premium sites which are in the top 1000 visited sites in the world~\cite{c3}. These facts can imply two things: 1. Publishers can't stop fake views/clicks alone. 2. Hackers are building sophisticated bots which emulates user characteristic that are tricking the current defense system.

If 25\% of artificial views happen on premium sites, this means the other 75\% are on armature or non-premium sites. Although it is unclear what defense systems the premium sites are using to defend against fake views, it is clear that the publishers alone can't stop fake views by themselves. In a recent study in 2014, 181 real video advertisements were observed over 60 days~\cite{c19}. The research found that 23\% of the views of advertisements came from bots. 67\% of the fake views came from residential homes and 58\% were using Microsoft Explorer 6, which has been discontinued since 2008~\cite{c19}. These facts imply that the hackers are infecting vulnerable computers and planting bots to generate artificial views on various advertisements. Indeed this was the case with “Operation Ghost Click” in 2011~\cite{c3, c4}. The U.S. FBI captured 6 Estonian Nationals who were installing rogue DNS servers to infect local DNS cache on vulnerable computers around the world. The rogue servers infected 4 million computers in 100 different countries, 500,000 in the U.S., to redirect users to various sites which hosted advertisements that were linked to the 6 Estonians~\cite{c4}. For example, if the infected computer browses “www.microsoft.com”, user would be redirected to a site that is similar to Microsoft’s site but with random advertisements. The 6 Estonians were able to illegally collect 14 million dollars from the advertisers~\cite{c4}.

@@

In this paper, we used 4 services that claim to generate view counts on videos hosted by YouTube and Dailymotion. The prices of their services ranged from 3 to 300 dollars and offered view counts from 50 to 50,000. We purchased the cheapest service ranging from 3 to 8 dollars for 500 to 5000 views. Only three services were able to deliver their view counts in span of 2 to 7 days while one service still haven't deliver as of May 4$^{th}$ 2015. The statistical data from YouTube and Dailymotion were limited; however, we did find some interesting data as well as verify some information that were stated in other research papers about fake views. Lastly, we wrote some programs which mimics the characteristics of traffics that were analyzed from services that generates view counts for monetary payment. Our programs were tested on videos hosted in YouTube.

@@

\subsection{Buildmyviews.org}
The first service that we used was from http://buildmyviews.org. The IP address of this website is 166.62.5.1, hosted by godaddy.com located in Scottsdale~\cite{c6} U.S. The site’s front page is displayed in figure 1 below. It doesn't look like a premium website but it does look legitimate but not actively managed. This service offered view counts for videos only hosted by YouTube, but they offered 3 different options of view counts.

@@

Aside from the view counts, this service also offered to generate comments on YouTube video. This website claims to offer 24/7 customer support via emails and also chat services. The chat services didn't seems to work as no one replied when we started to use their chat service screen. Moreover, when we sent an email asking about their basic operation on March 2, 2015, we didn't receive any reply as of April 2$^{nd}$, 2015. However, when we purchase their service of 1000 views for 3 dollars, we did receive a confirmation email from socialwarehouseorg@gmail.com with the name ``Kevin M''.

@@

The second service that we used was from http://portal.dalisocial.com/. The IP address of this website is 104.24.112.186, hosted by CloudFlare, Inc. located in San Francisco U.S. We needed to register before using the service but we used a random name and an email to get into the site. Email confirmation wasn't needed and this site didn't looked professionally managed. However, it offered services across different social media sites. This site offered but not limited to:

@@

The Dalisocial site did not offer granular services like buildmyviews.org. For example, it just offered one option to purchase 5000 YouTube views for 7 dollars within 3 days. We noticed the most of the link on the site didn't work. For example, nothing happened when we clicked the ``Contact Us'', ``About Us'', and ``Blog'' link. The only link that worked was the ``Login'' which directs to a page to purchase services. We did receive an email when we registered and purchase their service of 5000 views for 7 dollars. The email was from noreply@dalisocial.com.

@@

In this section, we analyzed data which was generated by the 3 services, since one vendor failed to deliver, that we mentioned in section III. We uploaded 4 different videos: 3 in YouTube and 1 in Dailymotion. All videos were about 60 seconds long and each were tested using different services. Since we can only use statistical data provided by YouTube and Dailymotion, there was limitation of data which could be observed and analyzed. For example, we couldn't observed the exact IP address but just the general physical location. However, we were able to observe key information such as average duration watched, method of access, what OS was used, and the view counts per day; to come up with the following analysis:

@@

\begin{enumerate}
  \item SocialWarrior.net used same or very similar type of bot from Buildmyviews.org to generate the views as we observe similar characteristics.
  \begin{itemize}
    \item Russia accounts for the highest number of views followed by Argentina.
    \item View length was different but still constant at 57 seconds.
    \item Used the same access method: ``YouTube watchpage''.
    \item All views used Blackberry OS.
  \end{itemize}
  \item The bots have viewed almost whole duration of the video hosted in YouTube, 57 seconds.
  \item It took significantly longer to deliver view counts on video hosted by Dailymotion. The 2000 view counts on YouTube was delivered in 48 hours while it took about a week to deliver view counts on Dailymotion.
  \item The view counts on Dailymotion wasn't generated systematically. We did not find a definite pattern but views were generated once or twice every 7-14 minutes for few hours, then go into a long pause, then start generating views again every 7-14 minutes.
\end{enumerate}

@@

\begin{enumerate}
  \item As already mentioned, SocialWarrior.net may used same or very similar type of bot from Buildmyviews.org as we observed similar characteristics.
  \item Assuming SocialWarrior,net and Buildmyviews.org used the same type of bot, the bots are flexible to view the whole or just part of the video.
  \item YouTube and Dailymotion use different system to count views. That is why it took only 48 hours to deliver 2000 views on YouTube while it took about a week to deliver only 500 views on Dailymotion.
  \item SocialWarrior.net used different methods to generate views on YouTube and Dailymotion. On Dailymotion, only the time can be observed, we didn't receive other data such as the source locaton, OS, and access method. However, based on the time data, SocialWarrior.net could have used real users to generate view counts on Dailymotion, as it isn't hard to generate 500 views in period of 7 days.
\end{enumerate}

@@

\begin{enumerate}
  \item The view sources were evenly distributed especially in the Middle East: Egypt, Saudi Arabia and Turkey (Fig. \ref{7a}).
  \item All bots viewed the entire video, 60 seconds.
  \item 51\% of views are from “YouTube homepage”, meaning, the video was accessed via link suggested by YouTube.  This is only possible if you have a YouTube account~\cite{c21}.
  \item 49\% of bot views are direct views, same method as previous 2 services used.
  \item 99\% of the traffic is from computers, mostly from Windows OS, but Mac and Linux also had small presence (less than 2\% each).
  \item 18 out of 5000 views from gaming consoles, from Saudi Arabia and Germany.
  \item 17 out of 5000 views from mobile devices; Android and IPhone but no Blackberry.
\end{enumerate}

@@

Here we tried to use our own code to generate artificial view counts on videos hosted in YouTube. Before writing the code, we studied how YouTube view counting system works. The following is the list of what we've learned:

@@

In order to generate YouTube views, we've tried publically available tools: PhantomJS and SeleniumHQ. PhamtonJS didn't work to generate views on YouTube since it doesn't support Adobe Flash Player; SeleniumHQ, however, was successful as it was tested on normal client machines as well as Ubuntu Server.

Since we didn't need the browser popup displaying YouTube videos, we used Xvfb (Virtual framebuffer X server for X Version 11) to buffer screen display in the background while taking snapshots for information analysis and debugging purposes.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=3.0in]{flowchart}
  \caption{Flowchart of our fake click generating code}
\end{figure}

Refer to our Github repository for the actual code (https://github.com/heronyang/youtube\_fake\_view). With our code, we were able to generate at most 301 view counts on videos hosted in YouTube, using one machine with one user agent. This is because YouTube view counting system analyzes the view counts after 301 and determined that the views generated by our code isn't from a real user. In our next section, we explain how we used our code in various ways to implement more user agents, unique IP addresses, and VPN connections to pass the 301 views on videos hosted in YouTube.

@@

We are assuming YouTube view counting system checks user agent information since this could be an obvious indicator to detect bot traffic. For example, it is highly unlikely that a video suddenly gets viewed 1000 times with the exact same user agent string. There are too many different OS/browser combination available for 1000 random users to have the same user string, and since one user wouldn't constantly view the same video 1000 times, this could be an obvious sign of bot traffic. Therefore, we tested our code using 526 different user agent strings to see if we can generate more than 301 artificial view counts on video hosted in YouTube.

@@

Setup environment where this experiment was executed:
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item OS: Ubuntu 14.01 LTS Server
  \item Duration: From April 28$^{th}$ 1930-2300 (3hr, 30min)
  \item Public IP: 172.31.20.23
  \item User agent: 526 different user agents
  \item 150-200 views every hour
\end{itemize}

@@

\subsubsection*{Findings}
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item View count quickly generated to 301 within one hour but unchanged as of May 4$^{th}$ 2015.
  \item 5 public IP addresses aren't enough to pass 301 view count.
\end{itemize}

@@

Setup environment where this experiment was executed:
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item OS: Mac OS X v10.10
  \item Duration: From April 30th 1730-0330 (10 hrs)
  \item Browser: Firefox 37.0.2
  \item 50-60 views every hour
\end{itemize}

\subsubsection*{Findings}
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item View count is still stuck at 301.
  \item Source IP is visible via flash browser plugin~\cite{c14}. This means that YouTube knows where the actual request is coming from; thus, anonymity isn't possible using TOR when viewing videos in YouTube.
\end{itemize}

@@

\subsubsection*{Findings}
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item View count is still stuck at 301.
  \item Using popular VPN connection doesn't matter.
\end{itemize}

@@

Lastly, YouTube counting system isn't perfect as it proven to allow both false positive and false negative view counts in our research. We were able to prove it allows false positive view counts by using the 4 services mentioned in section 2 \& 3. Moreover, for the videos that were stuck on 301+ views, we view the same videos manually and see if the view count will go over 301. The view counts didn't change even after we manually view the videos; therefore, we assume that YouTube’s counting
system is also vulnerable to false negative view counts.

@@

\begin{enumerate}
  \item The data provided by YouTube isn't enough to technically evaluate the characteristics of artificial view generating bots. The limitation of the data is already mentioned on Traffic Analysis section of the research. Perhaps, we could request granular statistical information from YouTube to provide the following:
  \begin{itemize}
    \item Exact time the views were generated
    \item The public source IP address
    \item User agent string for each view
  \end{itemize}
  \item We didn't have enough resources. As observed from the 3 artificial view generating services, bots were present from at least 20 different countries which was able to pass the 301 view count on YouTube video within 48 hours. Perhaps if we can partner with more VPN providers around the world, we can run our code in various places to see if we can also pass the 301 view count.
\end{enumerate}
